---
title: "Exam"
author: "Mark Klik & Misja Mikkers"
output: html_notebook
---

# Introduction

The exam consists of 2 parts. In the first part, you have to run a regression, test if the assumptions of a linear regression model are met, and make 2 graphs.

In the second part of the exam, you will have to make a map of Catholic and Protestant schools in the Netherlands.

# Packages

```{r}
library(tidyverse)
library(gvlma)
```

# Assignment 1

## Data

The data are given:

```{r}
set.seed(123)
df1 <- as.data.frame(matrix(runif(1*50, min = 1, max = 10), ncol = 1)) %>%
    mutate(epsilon = rnorm(50, mean = 0, sd = 2)) %>%
    mutate(response = 3 - 2* V1  + epsilon) %>%
    mutate(group = ifelse(V1 <= 5, 1,2))

```

## Asignment 1a

The first assigment is to make boxplot using ggplot with group on the x-axis and V1 on the y-axis.

```{r}
ggplot(df1, aes(x=group, y=V1)) + 
  geom_boxplot()

```
#### Explanation
I simply filled in the required information to make the requested boc plot.

## Assignment 1b

Run a regression with response variable as a function of V1.
Show the summary statistics of the regression.

```{r}
reg1 <- lm(data=df1, response~V1)
summary(reg1)
```
#### Explanation
I made a regression as requested

check if the assumptions of linear regression are met with the `gvlma()` function.

```{r}
gvlma(reg1)

```
#### Explanation
I filled in reg1 in gvlma() to see if the assumptions are met. They are met.

## Assignment 1c

Make a scatterplot with:

* V1 on the x-axis and the response on the y-axis
* Include the regression line in red with confidence interval 
* In a classic theme
* The x-axis should be labeled "Predictor", the y-axis should be labeled ("Response")


```{r}
'Predictor'<-df1['V1']
'Response'<-df1['response']
ggplot(df1,aes(x=Predictor,y=Response))+
  geom_point()+ theme_classic()+
  geom_smooth(method='lm',formula=y~x, col=10)
  

```
#### Explanation
I started with renaming V1 and response to Predictor and Response respectively. After which I made the desired graph using ggplot.

# Assigment 2

# Packages

```{r}
library(thematicmaps)
library(tidyverse)
```

## Assignment 2a

First you have to read in the file "nld_municipal_map.csv".
Hint: Look at the notebook of week 6 about maps.

```{r}
map_municipal <- 
  read.csv2("../Sourcedata/nld_municipal_map.csv", stringsAsFactors = FALSE, dec = ".")
head(map_municipal)
```
#### Explanation
Copied from the notebook from week 6

## Assignment 2b

Now you can make an empty map of the Netherlands.

```{r}
AddMapLayer(MapPlot(), map_municipal)

```
#### Explanation
Copied from the notebook from week 6

## Assignment 2c

Read in the pc4 locations (nld_pc4_locations.csv).

Hint: Don't forget the X and Y should be numeric variables!

```{r}
pc4_locations <- 
  read.csv2("../Sourcedata/nld_pc4_locations.csv", stringsAsFactors = FALSE, dec = ".") %>%
  mutate(X=as.numeric(as.character(X)))%>%
  mutate(Y=as.numeric(as.character(Y)))

str(pc4_locations)
```
#### Explanation
read the file and turned X and Y into numerics


## Assignment 2d

### 2di

Read in the school data

```{r}
schools <- read.csv2("../Sourcedata/schools.csv", stringsAsFactors = FALSE, dec = ".")
head(schools)
```
#### Explanation
read the file and used head to get a better view of what was in it

### 2dii

First, create a new dataframe schools1, which is equal to schools.

As you see POSTCODE has a structure of (1234 AB). You should create a new variable PC4 that is equal to the first 4 numbers in POSTCODE

Hint: Use the function `substr()`

Then select the variables PC4 and DENOMINATIE

```{r}
schools1 <- schools 
  schools1$PC4 <- substr('POSTCODE',1,4)
head(schools1)
  
```
#### Explanation
just tried things and ended up with this and got something that looked like the desired result...

### 2diii

Create the dataframe school_loc as a join from pc4_locations and school1 that combines the columns from both data frames, but only keeps rows where the value in the pc4_locations column matches in both data frames.
And then select the observations with DENOMINATIE is equal to "Rooms-Katholiek" or "Protestants-Christelijk"

```{r}
school_loc <- full_join(pc4_locations,schools1,by='DENOMINATIE')
```
#### Explanation
tried something without succes and ran out of time

## Assignment 2e

Create a map of Catholic and Protestant schools in the Netherlands


```{r}
AddMapLayer(MapPlot(), map_municipal) %>%
  AddPointsLayer(schools, sample_color, columnNameColor = "Type") 

```
#### Explanation
tried something without succes and ran out of time